\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex

Figure~\ref{fig:attack_model} shows the architecture of our attack model. \mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC. The details of each component in \tool are as follows.

>>>>

Figure~\ref{fig:attack_model} shows the architecture of our attack model. \circled[text=white,fill=myyellow]{\footnotesize{1}} represents the victim's devices; \circled[text=white,fill=myyellow]{\footnotesize{2}} is our \tool; \circled[text=white,fill=myyellow]{\footnotesize{3}} is the attacker's remote PC. The details of each component in \tool are as follows.
